Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
figs

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.7cm]{figs/Octa_mean}}
    {\includegraphics[width=2.7cm]{figs/Octa_gaussian}}
    {\includegraphics[width=2.7cm]{figs/Octa_k1}}
    {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
    {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
    {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{\emph{First row:} Mean, Gaussian, first and second principal curvature estimation on an OctaFlower with a digital domain of $130^3$.
  \emph{Second row:} First and second principal directions estimation (and zoom) on an OctaFlower.
  \emph{Third row:} Mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}

@@

We can first note that the required time for an object to compute ground truth
curvature is usually as high as the time required to extract the geometry and
compute all the above levels. Using approximations is thus mandatory, since for
big objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
computation is faster than the $l_0$ while results are enough close to the
$l_0$. For example, with $R=20$, the approximated visualization at $l_2$ takes
only 300ms while the $l_0$ visualization takes more than 4 seconds.

>>>>

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.2cm]{figs/Octa_mean}}
    {\includegraphics[width=2.2cm]{figs/Octa_gaussian}}
    % {\includegraphics[width=2.7cm]{figs/Octa_k1}}
    % {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
    % {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
    % {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{\emph{First row}: Mean and Gaussian curvature estimation, (zoom of) first and second principal directions estimation on an OctaFlower with a digital domain of $130^3$.
  % \emph{Second row:} (Zoom of) First and second principal directions estimation on an OctaFlower.
  \emph{Third row:} Mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}

@@

We can first note that the required time for an object to compute ground truth
curvature is usually as high as the time required to extract the geometry and
compute all the above levels. Using approximations is thus mandatory, since for
big objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
computation is faster than the $l_0$ while results are close enough. For
example, with $R=20$, the approximated visualization at $l_2$ takes only 300ms
while the $l_0$ visualization takes more than 4 seconds.
